Software architectures to integrate workflow engines in science gateways

### 2016-04-25 paper.tex

Architectures to integrate workflow engines in science gateways are
diagrammed in Figure~\ref{fig:architectures} using the graphical
notations shown in Figure~\ref{fig:notations}.
\note{Marc-e}{A few things bother me a bit with the notation fig., making it harder to assimilate
1- The interactions are padded in the middle of other stuff (Administrator, Data)
2- The Software component example says "Science gateway", should it not be empty?
3- The red arrow to explain the use of red; it looks like a very specific type 
of interactions instead of the desired "any interactions or components can be red meaning...",
especially with 'a' and 'd' which the reader does not know the meaning yet.
Maybe a little red arrow and square with "Red used when specific to workflow execution"?
I don't have a great solution...
4- Order in text jumps all over the fig notations. Explanations are given for, in order:
Components, workflow engine, interactions, abstract interactions, red color, tasks, data (no Administrator?)...
Could re-ordering the fig fix this? A figure figure legend could go a long way too (are there some in this journal?)
}

@@

\emph{Robustness of workflow execution} measures the likelihood that
workflow execution fails due to errors in the components or with the
interactions in the software architecture. Note that errors coming
from the infrastructure (e.g. unavailable data or terminated tasks) or
workflows (e.g., wrong user input or application errors) are not
covered since they do not stem directly from the software
architecture. Robustness is determined as the number of software
components and interactions that are specific to workflow execution,
which assumes that complex architectures tend to be prone to failure:
\begin{itemize}[leftmargin=0cm,itemindent=0.35cm,itemsep=0cm]
\item Components (\texttt{R$_1$}): number of specific components
  involved in workflow executions. Science
gateway, for instance, is \emph{not} specific to workflow execution
since it is used to authenticate users, add new workflows, transfer
\item Interactions (\texttt{R$_2$}): number of specific interactions
  involved in workflow executions.
\end{itemize}
These specific components and interactions are represented in red in
the architecture diagrams in
Figure~\ref{fig:architectures}. \texttt{R$_1$} and \texttt{R$_2$}  are summed to obtain the total score for this
criterion, which measures the total number of software pieces that are
specifically involved in workflow execution.

>>>>

Architectures to integrate workflow engines in science gateways are
diagrammed in Figure~\ref{fig:architectures} using the graphical
notations shown in Figure~\ref{fig:notations}.
\note{Marc-e}{A few things bother me a bit with the notation fig., making it harder to assimilate
1- The interactions are padded in the middle of other stuff (Administrator, Data)
2- The Software component example says "Science gateway", should it not be empty?
3- The red arrow to explain the use of red; it looks like a very specific type
of interactions instead of the desired "any interactions or components can be red meaning...",
especially with 'a' and 'd' which the reader does not know the meaning yet.
Maybe a little red arrow and square with "Red used when specific to workflow execution"?
I don't have a great solution...
Red has special meaning, maybe remove it from the other pics (workflow eng, tasks)
as it creates lots of visual interference when looking for red?
4- Order in text jumps all over the fig notations. Explanations are given for, in order:
Components, workflow engine, interactions, abstract interactions, red color, tasks, data (no Administrator?)...
Could re-ordering the fig fix this? A figure figure legend could go a long way too (are there some in this journal?)
}

@@

\emph{Robustness of workflow execution} measures the likelihood that
workflow execution fails due to errors in the components or with the
interactions in the software architecture. Note that errors coming
from the infrastructure (e.g. unavailable data or terminated tasks) or
workflows (e.g., wrong user input or application errors) are not
covered since they do not stem directly from the software
architecture. Robustness is determined as the number of software
components and interactions that are specific to workflow execution,
which assumes that complex architectures tend to be prone to failure:
\begin{itemize}[leftmargin=0cm,itemindent=0.35cm,itemsep=0cm]
\item Components (\texttt{R$_1$}): number of specific components
  involved in workflow executions. Science
gateway, for instance, is \emph{not} specific to workflow execution
since it is used to authenticate users, add new workflows, transfer
user data, etc.
\item Interactions (\texttt{R$_2$}): number of specific interactions
  involved in workflow executions.
\end{itemize}
These specific components and interactions are represented in red in
the architecture diagrams in
Figure~\ref{fig:architectures}. \texttt{R$_1$} and \texttt{R$_2$}  are summed to obtain the total score for this
criterion, which measures the total number of software pieces that are
specifically involved in workflow execution.
